---
title: "Parleh Host Report"
output:
  word_document: default
  pdf_document: default
  html_notebook: default
---

#### Data Import
```{r}
library(tidyverse)# Load base packages manually

pacman::p_load(pacman, rio) 

# CSV
crina <- import("/Users/tmane/OneDrive/Desktop/twitterscrap/crinatwitterdata.csv")
james <- import("/Users/tmane/OneDrive/Desktop/twitterscrap/jamessharmantwitterdata.csv")
michael <- import("/Users/tmane/OneDrive/Desktop/twitterscrap/michaelsinghtwitterdata.csv")
noor <- import("/Users/tmane/OneDrive/Desktop/twitterscrap/noortwitterdata.csv")

```

## Crina - @crinamm

##### Crina's Twitter Stats
Followers: 3,179
Following: 908

Crina posts a high volume of tweets every month. At the end of April and in the month of May, she posted over 1,400 tweets, and over 1000 in June. 

* In May she garnered 7096 likes, 880 replies, and 418,172 retweets.
* In June she garnered 4978 likes, 588 replies, and 149,205 retweets.
* So far, in July she has garnered 543 likes, 60 replies, and 33998 retweets.

A majoirty of her content consists of WNBA, tennis, and Parleh/Fanduel retweets.

```{r}
noor %>%
  filter(created_at > "2022-06-30") %>%
  summarise(
    likes = sum(likes),
    replies = sum(replies),
    retweets = sum(retweets)    
    )
```
```{r}
#Number of Tweets Each Month
crina_monthly_tweets <- tribble(
  ~Month,         ~Tweets,
  "May",       1418,
  "June",       1093,
  "July",        114,
)

ggplot(data = crina_monthly_tweets, aes(x = Month, y = Tweets, stat = "identity")) +
  geom_col(color = "black") +
  geom_text(aes(label = Tweets),
      position = position_stack(vjust = 0.5)) + 
  coord_polar(theta = "y") + 
  ggtitle("Crina - Tweets Posted Per Month")

            
```

```{r}
#Tweets Posted Per Day

ggplot(crina, aes(created_at))+
geom_freqpoly(binwidth = 86400) +
ggtitle("Crina - Tweets Posted Per Day")
```
Crina's high volume of twitter activity is advantageous for the Parleh. Crina has a regular cadence of content that she posts everyday that our audience can count on and look forward to (engaging in Twitter activity 40 times a day on average). 

Crina also retweets a majority of the Parleh's content everyday. In turn, our content is being amplified to an additional 3,180 followers, and increases the chances of more engagement and impressions.

```{r}
#Likes per Tweet
data <- crina %>%
  rownames_to_column(var="likes")

ggplot(data = crina) + 
  geom_point(mapping = aes(x = created_at, y = likes), position = 'jitter') +
  ggtitle("Crina - Likes Per Tweet") + 
  geom_label( 
    data=crina %>% filter(created_at>'2022-04-15' & likes>200), # Filter data first
    aes(x = created_at, y = likes,label=likes)
  )

```

Above, I have highlighted Crina's top performing tweets in terms of likes. 
* Out of her top 9 most engaging tweets, 7 of them were about the WNBA
* All of the tweets included an attached video, GIF, or image
* All of the tweets had over 10 replies; sparked a discussion relevant to her content
  * This is something we should aim to replicate with Crina under the Parleh brand. (Try and spark a converstaion in our comment section)

### Most Engaging Tweets

```{r}
#Most Engaging Tweets
crina_smaller <- transmute(crina, created_at, likes, replies, retweets, engagements = (likes + replies + retweets), text) 

arrange(crina_smaller, desc(likes))
```

```{r}
#Likes Per Month

crina_monthly_likes <- tribble(
  ~Month,        ~Likes,
  "July",       543,
  "June",       4978,
  "May",       7096,
  
)

ggplot(data = crina_monthly_likes) +
  geom_bar(mapping = aes(x = Month, y = Likes), stat = "identity") + 
  geom_label( 
    data=crina_monthly_likes %>% filter(Likes>0), # Filter data first
    aes(x = Month, y = Likes,label=Likes)
  ) +
  ggtitle("Crina - Likes Per Month")
```
### Engagement Distribution

```{r}
#Distribution of Likes
crina_smaller <- select(crina, created_at, likes, replies, retweets) %>%
  mutate(crina, engagements = (likes + replies + retweets) )


crina_smaller %>%
  filter(engagements < 201) %>%
  ggplot(aes(x=engagements)) +
    geom_histogram(binwidth = 20) +
  ggtitle("Crina - Engagement Distribution")
      
```
Above shows the distribution of Crina's total engagements (likes + replies + retweets). A majoirty of her tweets garner 0-25 total engagements, which is common for her follower count.


## James - @jamessharman

##### James' Twitter Stats
Followers: 16,093
Following: 1,805

James posts a relatively low volume of tweets each month compared to Crina. At the end of April and in the month of May, he posted 135 tweets, and 134 in June. 

* In May he garnered 1266 likes, 187 replies, and 1325 retweets.
* In June he garnered 1050 likes, 120 replies, and 366 retweets.
* So far, in July she has garnered 62 likes, 7 replies, and 27 retweets.

James' Twitter content consists of mainly soccer content; and reposting Parleh and Footy Prime content.

```{r}
#Number of Tweets Each Month
james_monthly_tweets <- tribble(
  ~Month,         ~Tweets,
  "May",       134,
  "June",       135,
  "July",        14,
)

ggplot(data = james_monthly_tweets, aes(x = Month, y = Tweets, stat = "identity")) +
  geom_col(color = "black") +
  geom_text(aes(label = Tweets),
      position = position_stack(vjust = 0.5)) + 
  coord_polar(theta = "y") + 
  ggtitle("James - Tweets Posted Per Month")
  

```
```{r}
#Tweets Posted Per Day
james_smaller <- filter(james, created_at > "2022-04-30")

ggplot(james_smaller, aes(created_at))+
geom_freqpoly(binwidth = 84600) +
ggtitle("James - Tweets Posted Per Day")
```
James is currently averaging about 4.5 tweets per day. This is actually above the U.S. average for tweets per day. The top 25% tweeters in the U.S. (in terms of volume) tweet about 2.1 times per day.

```{r}
#Likes per Tweet


ggplot(data = james_smaller) + 
  geom_point(mapping = aes(x = created_at, y = likes), position = 'jitter') +
  ggtitle("James - Likes Per Tweet") + 
  geom_label( 
    data=crina %>% filter(created_at>'2022-04-30' & likes>200), # Filter data first
    aes(x = created_at, y = likes,label=likes)
  )

```
Above, I have highlighted James' top performing tweets in terms of likes. 
* Out of her top 9 most engaging tweets, 7 of them were about soccer
* All of the tweets included an attached video, GIF, or image
* Almost all of the tweets were amplified/amplifying another account; shared media

### Most Engaging Tweets

```{r}
#Most Engaging Tweets
james_engage <- transmute(james, created_at, likes, replies, retweets, engagements = (likes + replies + retweets), text) 

arrange(james_engage, desc(likes))
```

```{r}
#Likes Per Month

james_monthly_likes <- tribble(
  ~Month,        ~Likes,
  "July",       62,
  "June",       1050,
  "May",       1252,
  
)

ggplot(data = james_monthly_likes) +
  geom_bar(mapping = aes(x = Month, y = Likes), stat = "identity") + 
  geom_label( 
    data=james_monthly_likes %>% filter(Likes>0), # Filter data first
    aes(x = Month, y = Likes,label=Likes)
  ) +
  ggtitle("James - Likes Per Month")
```
### Engagement Distribution

```{r}
#Distribution of Likes
james_small <- select(james, created_at, likes, replies, retweets) %>%
  mutate(james, engagements = (likes + replies + retweets) )


james_small %>%
  filter(engagements < 201) %>%
  ggplot(aes(x=engagements)) +
    geom_histogram(binwidth = 20) +
  ggtitle("James - Engagement Distribution")
      
```
Above shows the distribution of James' total engagements (likes + replies + retweets). A majoirty of his tweets garner 0-25 total engagements, which is common for his follower count.


## Noor - @noorrzainab

##### Noor's Twitter Stats
	
Followers: 10,244
Following: 1,154

At the end of April and in the month of May, Noor posted over 308 tweets, and 324 tweets in June. 

* In May she garnered 7627 likes, 446 replies, and 48320 retweets.
* In June she garnered 6093 likes, 380 replies, and 2669 retweets.
* So far, in July she has garnered 6,139 likes, 145 replies, and 1612 retweets.

A majority of her content consists of NBA related tweets, and Parleh 3-Point Line/General content retweets.

```{r}
#Number of Tweets Each Month
noor_monthly_tweets <- tribble(
  ~Month,         ~Tweets,
  "May",       308,
  "June",       324,
  "July",        51,
)

ggplot(data = noor_monthly_tweets, aes(x = Month, y = Tweets, stat = "identity")) +
  geom_col(color = "black") +
  geom_text(aes(label = Tweets),
      position = position_stack(vjust = 0.5)) + 
  coord_polar(theta = "y") + 
  ggtitle("Noor - Tweets Posted Per Month")
            
```
```{r}
#Tweets Posted Per Day
noor_smaller <- filter(noor, created_at > "2022-04-30")

ggplot(noor_smaller, aes(created_at))+
geom_freqpoly(binwidth = 84600) +
ggtitle("Noor - Tweets Posted Per Day")
```
James is currently averaging about 10 tweets per day. Noor Posts a high volume of tweets, and is consistant at amplifying Parleh content everday. Thus, we need to figure out how we can drive Noor's twitter engagement to the Parleh's profile.



```{r}
#Likes per Tweet

ggplot(data = noor_smaller) + 
  geom_point(mapping = aes(x = created_at, y = likes), position = 'jitter') +
  ggtitle("Noor - Likes Per Tweet") + 
  geom_label( 
    data=noor %>% filter(created_at>'2022-04-30' & likes>200), # Filter data first
    aes(x = created_at, y = likes,label=likes)
  )

```
Above, I have highlighted Noor's top performing tweets in terms of likes.
* Noor is the only content creator at the Parleh that can hit a likes account > 1000 consistently
* Many of her top tweets did not have a video or image attached to it
  * Example - Noors Top Tweet "If there’s anyone you wanna be down 0-2 to it’s doc rivers"
    * 19.5k likes
    * 222 Quote Tweets
    * 1,090 Retweets
  * Even though she didnt attach video content, she was able to spark a conversation and engagement in replies to her tweet.


### Most Engaging Tweets

```{r}
#Most Engaging Tweets
noor_engage <- transmute(noor, created_at, likes, replies, retweets, engagements = (likes + replies + retweets), text) 

arrange(noor_engage, desc(likes)) 
```
```{r}
#Likes Per Month

noor_monthly_likes <- tribble(
  ~Month,        ~Likes,
  "July",       6145,
  "June",       6093,
  "May",       7627,
  
)

ggplot(data = noor_monthly_likes) +
  geom_bar(mapping = aes(x = Month, y = Likes), stat = "identity") + 
  geom_label( 
    data=noor_monthly_likes %>% filter(Likes>0), # Filter data first
    aes(x = Month, y = Likes,label=Likes)
  ) +
  ggtitle("Noor - Likes Per Month")
```

### Engagement Distribution

```{r}
#Distribution of Likes
noor_small <- select(noor, created_at, likes, replies, retweets) %>%
  mutate(noor, engagements = (likes + replies + retweets) )


noor_small %>%
  filter(engagements < 201) %>%
  ggplot(aes(x=engagements)) +
    geom_histogram(binwidth = 50) +
  ggtitle("Noor - Engagement Distribution")
      
```
Above shows the distribution of Noors' total engagements (likes + replies + retweets). A majoirty of her tweets garner 0-50 total engagements. She also has about 300 Tweets that attained over 500 engagements.